\documentclass[11pt]{res} % default is 10 pt
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textheight}{9.5in} % increase text height to fit resume on 1 page
\newsectionwidth{0pt}  % So the text is not indented under section headings
\renewcommand\labelitemi{--}
\usepackage{multicol}
\usepackage{lipsum}
\usepackage{hanging}

\begin{document} 
	\begin{center}
 		\textbf{\LARGE Hugh McCreery} \\
 		hugh.mccreery.jobs@gmail.com $\cdot$ (720) 326-5513 $\cdot$ https://github.com/hbmccreery
	\end{center}
\vspace{-0.6in}
\begin{resume}
\hrulefill
\vspace{-0.2in}                                  
\section{EDUCATION} 
 \noindent COLORADO SCHOOL OF MINES, Golden, CO \hfill May 2019 \\
B.S., \textit{magna cum laude}, Applied Mathematics - Statistics\\
Minor in Computer Science \\
Dean's List \hfill Fall 2015 - Spring 2019 \\
\vspace{-0.1in}
\hrulefill
\vspace{-0.1in}  
\section{EXPERIENCE} 
DATA SCIENTIST, SPORTRADAR \hfill July 2022 - Present \\
Remote

DATA SCIENTIST, BASEBALL ANALYTICS \hfill May 2019  - July 2022	\\
Baltimore Orioles, Baltimore, MD

\begin{itemize}
	\item Used machine learning techniques in R and Python to convert player tracking data into metrics used in decision making.
	\item Create data pipelines using Python and Amazon SQS.
	\item Designed tools to help users access and analyze data through Django and React.
	\item Created interactive data visualizations with React and d3.js.
	\item Scraped and maintained a variety of 3rd party datasets with Python.
\end{itemize}
\vspace{-0.15in}  
DATA SCIENCE DEVELOPER INTERN \hfill Summer 2018 \\
Arrow Electronics, Centennial, CO

\begin{itemize}
	\item Created a proof-of-concept product recommender system using Python to improve relevance of current recommendations to customers.
	%\item Analyzed inventory data with Python to improve resource management and predict slow moving inventory.
	\item Used Agile principles to manage requests of business users.
\end{itemize}
\vspace{-0.15in}  
STUDENT ASSISTANT - CONTROLLER'S OFFICE \hfill Fall 2017 - Summer 2019 \\
Colorado School of Mines, Golden, CO 

\begin{itemize} 
	\item Assisted in maintenance of queries used in reporting.
\end{itemize}

\vspace{-0.2in}
\hrulefill
\vspace{-0.2in}  
\section{SKILLS}

\begin{itemize} 
	\item Creating clean and maintainable code in Python and R (tidyverse)
	\item Providing clear visualizations of data using ggplot2, matplotlib, and d3.js
	\item Construction of machine learning models within tidymodels and scikit-learn
	\item Experience with relational (PostgreSQL) and non-relational (MongoDB) databases
	\item Creating professional documents in \LaTeX
\end{itemize}

\vspace{-0.2in}
\hrulefill
\vspace{-0.2in}  

\section{PROJECTS}
\begin{hangparas}{.25in}{1}
NFL BIG DATA BOWL \hfill January 2021 \\
Used state-of-the-art player tracking data provided by the NFL to evaluate defensive skills and produced a shiny application to present results to potential decision makers.
	\vspace{-0.15in}  
	
CAPSTONE - OZONE POLLUTION \hfill Spring 2019	\\
Worked with NOAA to conduct research on a newly created dataset detailing global surface level ozone pollution. Examined the relationship between national economic growth and ozone pollution levels and used change point analysis to determine areas with significantly improving or worsening conditions.
\vspace{-0.15in}  

\end{hangparas}
\end{resume}
\end{document}


SPATIAL STATISTICS - MERCURY POLLUTION ANALYSIS \hfill Fall 2018 \\ \indent Implemented kriging methods in R to analyze mercury pollution data from the NADP and predict locations with potentially problematic levels of pollution outside of the dataset.

DATA SCIENCE - STATCAST MODELLING \hfill Spring 2018 \\ \indent Utilized MLB's new Statcast database alongside machine learning techniques in Python to model hit probabilities given the information on path of the ball and create a new metric for player performance


MATHEMATICAL BIOLOGY - DIABETIC GLUCOSE DYNAMICS \hfill Spring 2017 \\ Examined existing models of insulin and glucose secretion in diabetics, introduced new parameters to more accurately represent the impact of diabetes on insulin-producing cells, and used MATLAB to examine the impacts of these new terms

\vspace{-0.15in}  



COLORADO ROCKIES CASE COMPETITION \hfill Winter 2017 \\ Developed approximate valuations of each selection in the MLB draft and presented findings to members of the Rockies front office as a finalist of the competition.


\section{RELEVANT COURSEWORK}
\vspace{0.05in}
\begin{multicols}{2}
	\setlength{\columnsep}{0cm}
	\noindent
	\begin{itemize}
		\item CSCI 470 - Machine Learning
		\item CSCI 403 - Database Management
		\item MATH 432 - Spatial Statistics
		\item MATH 438 - Stochastic Models
	\end{itemize}
\end{multicols}

\noindent \raggedright{hugh.mccreery.jobs@gmail.com}\\ \textbf{\LARGE Hugh McCreery}\\ \raggedleft{(720) 326-5513}






